Stellar Bars in Isolated Gas-Rich Galaxies Do Not Slow Down

### 2022-04-19 paper/ms.tex
Add circular velocity to methods

Our setup is initially out of equilibrium, but we found that after
$\sim500\,\textrm{Myr}$, the entire system has settled into a steady-state
configuration and initial transients appear not to affect the results after
this point. The constant surface density of the initial gas disk is important
for ensuring the gas disk is dense enough in order for comparisons to real
galaxies to be appropriate. We plot the circular velocity curve in Extended
Data Fig.~\ref{fig:vcirc} compared to observational
estimates.\cite{2019ApJ...871..120E} Our disk is slightly more massive than
the Milky Way disk, and in the SMUGGLE run the addition of the gas phase
results in a slightly higher circular velocity. We also show the evolution of
the surface density profile in Extended Data Fig.~\ref{fig:surf} compared to
observational estimates (CITE).

>>>>

Our setup is initially out of equilibrium, but we found that after
$\sim500\,\textrm{Myr}$, the entire system has settled into a steady-state
configuration and initial transients appear not to affect the results after
this point. The constant surface density of the initial gas disk is important
for ensuring the gas disk is dense enough in order for comparisons to real
galaxies to be appropriate.

We computed the circular velocity curve of our model using the \texttt{AGAMA}
package.\cite{2019MNRAS.482.1525V} We fit the baryonic component (stellar
disk, bulge, gas, and newly formed stars) with an axisymmetric cylindrical
spline with $20$ grid points in both the radial and vertical direction
spanning $0.2$ to $50\,\textrm{kpc}$ in the radial direction and from $0.02$
to $10\,\textrm{kpc}$ in the vertical direction. We fit the dark matter halo
using a spherically symmetric multipole fit with a maximum angular harmonic
coefficient of $l=2$. We plot the circular velocity curve in Extended Data
Fig.~\ref{fig:vcirc} compared to observational
estimates.\cite{2019ApJ...871..120E} Our disk is slightly more massive than
the Milky Way disk, and in the SMUGGLE run the addition of the gas phase
results in a slightly higher circular velocity. We also show the evolution of
the surface density profile in Extended Data Fig.~\ref{fig:surf} compared to
observational estimates.\cite{2012ARAA..50..531K}
